---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Sydney Brougham"
date: "8/26/2019"
output: 
  html_document: 
    fig_width: 5
    highlight: haddock
    theme: cerulean
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

### Exercise 1
The datasaurus_dozen file has 1846 rows and 3 columns. The variables are 'dataset', 'x', and 'y'.

### Exercise 2
First let's plot the data in the dino dataset:
```{r plot-dino}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:
```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
r = -0.0645

### Exercise 3
Plot the data in the star dataset:
```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Correlation coefficient between x and y in star dataset:
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

This correlation coefficient for star is very close to that of the dino dataset, slightly higher.

### Exercise 4
```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient for the circle dataset is also very close that of the dino dataset, slightly lower.

### Exercise 5
Plot all the datasets at once.
```{r plot-all, fig.height=10, fig.width=6}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

Generate the correlation coefficients for all the datasets.
```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```



